
**HW#12 : Advanced ggplotting**   
01 May 2020   
LKS   

1. For this exercise, use your newly-developed ggplot chops to create some nice graphs from your own data (If you do not have a good data frame to use for graphics, use one of the many built-in data frames from R (other than mpg, which we are using in class)). Experiment with different themes, theme base sizes, aesthetics, mappings, and faceting. When you are finished, try exporting them to high quality pdfs, jpgs, eps files, or other formats that you would use for submission to a journal.

First graphing attempt at creating an empty, interesting looking map (not for my own data publication)

```{r message = FALSE}
library(rworldmap)
library(rworldxtra)
library(ggmap)
library(ggplot2)
library(wesanderson)

micra <- read.csv("North_American_Micrathena.csv")


Car <- c(left = -110, bottom=6, right=-60, top=35) #set frame w/ lat and long 
get_stamenmap(Car, zoom=4, maptype="watercolor") %>% ggmap() #pipe map type into ggmap framework 

#obviously ugly coloration, but I liked it for this exercise
```
Create a map of collection localities for *Micrathena* species 
```{r message=FALSE}
qmplot(Longitude, Latitude, data=micra, zoom=5, source = "stamen", maptype = "toner-lite", legend = "left", extent = "devicee", padding=0.2, color=Species, main="Collection Localities of North American and Caribbean Micrathena") + theme(plot.title = element_text(hjust=0.5))
```

Stacked bar plots of species collected per country or region 
```{r}
#Bar Plot of species records/ country
species_per_co <- table(micra$Species,micra$Location)
species_per_co <- data.frame(species_per_co)
colnames(species_per_co) <- c("Species", "Location", "Freq")

#Using wes anderson color palette 
ggplot(data = species_per_co, aes(fill=Species, y=Freq, x=Location)) + scale_fill_manual(values=wes_palette(n=9, "FantasticFox1", type= "continuous")) + geom_bar(position = "stack", stat = "identity") + ggtitle("Species of Micrathena collected per region") + theme_minimal(base_size = 10, base_family = "serif") + theme(plot.title = element_text(hjust=0.5), legend.title = element_text(face="bold"), legend.text = element_text(face="italic"), axis.text.x = element_text(size=4.5)) 

#Could facet wrap but locations are tricky to read
ggplot(data = species_per_co, aes(fill=Species, y=Freq, x=Location)) + scale_fill_manual(values=wes_palette(n=9, "FantasticFox1", type= "continuous")) + geom_bar(position = "stack", stat = "identity") + ggtitle("Species of Micrathena collected per region") + theme_minimal(base_size = 10, base_family = "serif") + theme(plot.title = element_text(hjust=0.5), axis.text.x = element_text(size=4.5)) + facet_wrap(~Species, scales = "free_x") + theme(strip.text.x = element_text(size=10, face='italic'), legend.text=element_text(face="italic"))

```

