---
title: 'Homework #6'
author: "Lily Shapiro"
date: "2/19/2020"
output: html_document
---
```{r}
library(ggplot2) # for graphics
library(MASS) # for maximum likelihood estimation
```
#Data
```{r}
z <- read.table("LLAS.cwu.igs08.csv", header=TRUE,sep=',',stringsAsFactors = FALSE)
str(z)
summary(z)
```

quick and dirty, a truncated normal distribution to work on the solution set
```{r}
z <- data.frame(z)
names(z) <- list("ID","myVar")
z <- z[z$myVar>0,]
str(z)
summary(z$myVar)
```
#Data Histogram
```{r}
p1 <- ggplot(data=z, aes(x=Vertical..mm.,y=..density..)) + geom_histogram(color="grey60",fill="cornsilk",size=0.2)
print(p1)
```

#Empirical Density

```{r}
p1 <-  p1 + geom_density(linetype="dotted",size=0.75, )
print(p1)
```
#ML Parameters

```{r}
normPars <- fitdistr(z$Vertical..mm.,"normal")
print(normPars)
str(normPars)
normPars$estimate["mean"] # note structure of getting a named attribute
```

#Normal Probability Density
```{r}
meanML <- normPars$estimate["mean"]
sdML <- normPars$estimate["sd"]

xval <- seq(0,max(z$Vertical..mm.),len=length(z$Vertical..mm.))

stat <- stat_function(aes(x = xval, y = ..y..), fun = dnorm, colour="red", n = length(z$Vertical..mm.), args = list(mean = meanML, sd = sdML))
p1 + stat
```

#Exponential probability density
```{r}
expoPars <- fitdistr(z$Vertical..mm.,"exponential")
rateML <- expoPars$estimate["rate"]

stat2 <- stat_function(aes(x = xval, y = ..y..), fun = dexp, colour="blue", n = length(z$Vertical..mm.), args = list(rate=rateML))
 p1 + stat + stat2
```
Some values in my vertical distance category were negative (to represent sinking), which are incompatible with a Exponential probability density, so values less than 0 are ignored, resulting in this (interesting) curve
#Uniform probability density 
```{r}
stat3 <- stat_function(aes(x = xval, y = ..y..), fun = dunif, colour="darkgreen", n = length(z$Vertical..mm.), args = list(min=min(z$Vertical..mm.), max=max(z$Vertical..mm.)))
p1 + stat + stat2 + stat3
```
#Gamma probability density
```{r}
gammaPars <- fitdistr(z$Vertical..mm.,"gamma")
shapeML <- gammaPars$estimate["shape"]
rateML <- gammaPars$estimate["rate"]

stat4 <- stat_function(aes(x = xval, y = ..y..), fun = dgamma, colour="brown", n = length(z$Vertical..mm.), args = list(shape=shapeML, rate=rateML))
p1 + stat + stat2 + stat3 + stat4
```
Same situation for gamma probability curve as exponential 
#Beta probability density
```{r}
pSpecial <- ggplot(data=z, aes(x=z$Vertical..mm./(max(z$Vertical..mm. + 0.1)), y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) + 
  xlim(c(0,1)) +
  geom_density(size=0.75,linetype="dotted")

betaPars <- fitdistr(x=z$Vertical..mm./max(z$Vertical..mm. + 0.1),start=list(shape1=1,shape2=2),"beta")
shape1ML <- betaPars$estimate["shape1"]
shape2ML <- betaPars$estimate["shape2"]

statSpecial <- stat_function(aes(x = xval, y = ..y..), fun = dbeta, colour="orchid", n = length(z$myVar), args = list(shape1=shape1ML,shape2=shape2ML))
pSpecial + statSpecial
```
